Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-11-22 documentation/authors.tex
Lots of changes from review
Added footnotes for authors
Addressed lots and lots of comments
More edits

\author[1]{B.~Matusch}
\affil[1]{SNOLAB, Lively, Ontario, P3Y 1N2, Canada}

@@

\author[4]{I.~J.~Arnquist}
\affil[5]{Pacific Northwest National Laboratory, Richland, Washington 99354, USA}

\author[4]{D.~M.~Asner}

@@

\author[2]{U.~Chowdhury}

@@

@@

@@

@@

@@

\author[5]{J.~Zhang}

>>>>

\author[1]{B.~Matusch \thanks{Corresponding: \url{brendon.matusch@snolab.ca}}}
\affil[1]{SNOLAB, Lively, Ontario, P3Y 1N2, Canada}

@@

\author[4]{I.~J.~Arnquist}
\affil[4]{Pacific Northwest National Laboratory, Richland, Washington 99354, USA}

\author[4]{D.~M.~Asner \thanks{now at Brookhaven National Laboratory}}

@@

\author[2]{U.~Chowdhury \thanks{now at Canadian Nuclear Laboratories}}

@@

\author[4]{C.~Cowles}

@@

\author[4]{C.~M.~Jackson}

@@

\author[4]{B.~Loer}

@@

\author[4]{K.~Wierman}

@@

\author[5]{J.~Zhang \thanks{Argonne National Laboratory}}

### 2018-11-22 documentation/paper.tex
More edits

@@

The first step is to calculate the standard deviation $S$ of the union of $N$ and $A$. This gives an indication of the scale of the overall distribution. When $N$ and $A$ are divided by $S$, they are normalized so that the standard deviation of their union is equal to 1. While the neural network’s outputs are bounded in the range of 0 to 1 with a sigmoid activation on the last layer, AP has a significantly wider range. Normalization of the union prevents this from creating a bias where AP would produce a higher standard deviation with a similarly proportioned error.

The second step is to calculate the mean of the standard deviations of the normalized sets of neutrons and alpha particles individually. This is an indication of how tightly clustered or widely dispersed the discriminator’s predictions are for each class. Very consistent predictions of $x$ for neutrons and $y$ for alphas (for any given $x$ and $y$), with minimal variance off those specific values, will produce a low class-wise standard deviation.

@@

(Note that in Figure \ref{grav_grid_search}, AP is normalized differently than in the original PICO-60 study. In this normalized spectrum, the decision boundary between neutrons and alpha particles is at 0.25.)

>>>>

\DeclareUnicodeCharacter{0301}{'}

@@

The first step is to calculate the standard deviation $S$ of the union of $N$ and $A$. This gives an indication of the scale of the overall distribution. When $N$ and $A$ are divided by $S$, they are normalized so that the standard deviation of their union is equal to 1. While the neural network's outputs are bounded in the range of 0 to 1 with a sigmoid activation on the last layer, AP has a significantly wider range. Normalization of the union prevents this from creating a bias where AP would produce a higher standard deviation with a similarly proportioned error.

The second step is to calculate the mean of the standard deviations of the normalized sets of neutrons and alpha particles individually. This is an indication of how tightly clustered or widely dispersed the discriminator's predictions are for each class. Very consistent predictions of $x$ for neutrons and $y$ for alphas (for any given $x$ and $y$), with minimal variance off those specific values, will produce a low class-wise standard deviation.

@@

Note that in Figure \ref{grav_grid_search}, AP is normalized using a similar method to the original PICO-60 study \cite{pico}. In this normalized spectrum, the decision boundary between neutrons and alpha particles is at 0.25.
